Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-11-12 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper

@@

df_aoi_long <- df_aoi_filtered %>%
  rowwise() %>%
  mutate(
    across(starts_with("Number_of_fixations"), ~ .x / Duration_of_interval_min, .names = "fixation_per_min_{.col}")
  ) %>%
  ungroup() %>%
  pivot_longer(
    cols = starts_with("fixation_per_min_Number_of_fixations"),
    names_to = "AOI",
    values_to = "Fixations_per_minute"
  ) %>%
  mutate(AOI = str_remove(AOI, "fixation_per_min_Number_of_fixations.")) %>%
  mutate(AOI = factor(AOI, levels = c("All", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
                                      "Board_Screen", "Material_Teacher", "Material_Students", 
                                      "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"))) %>%
  arrange(AOI)

@@

knitr::kable(nof.table,
             caption = "N, M, SD, min & max number of fixation per minute (across all AOIs)")

@@

# Filtere und wähle die relevanten Spalten aus
df_aoi_filtered <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations")
  )

# Erstelle die AOI "Students" durch Summieren der Werte für Anna, Bianca und Carl(a)
df_aoi_filtered <- df_aoi_filtered %>%
  mutate(
    Total_duration_of_fixations.Students = 
      `Total_duration_of_fixations.Anna` +
      `Total_duration_of_fixations.Bianca` +
      `Total_duration_of_fixations.Carl(a)`,
    Number_of_fixations.Students = 
      `Number_of_fixations.Anna` +
      `Number_of_fixations.Bianca` +
      `Number_of_fixations.Carl(a)`
  )

# Berechne die durchschnittliche Fixationsdauer für jede AOI individuell (einschließlich "Disruptive_Person")
df_aoi_avg_long <- df_aoi_filtered %>%
  pivot_longer(
    cols = starts_with("Total_duration_of_fixations") | starts_with("Number_of_fixations"),
    names_to = "Measure_AOI",
    values_to = "Values"
  ) %>%
  separate(Measure_AOI, into = c("Measure", "AOI"), sep = "\\.", extra = "merge") %>%
  pivot_wider(
    names_from = Measure,
    values_from = Values
  ) %>%
  mutate(
    Average_duration = round(Total_duration_of_fixations / Number_of_fixations, digits = 2)
  )

# Berechne `Average_duration_mtu` und `Number_fixation_mtu` durch Aufsummieren der Fixationsdauer und -anzahl, ohne "Disruptive_Person"
df_mtu_summary <- df_aoi_filtered %>%
  rowwise() %>%  # Zeilenweise Berechnung
  mutate(
    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations")), na.rm = TRUE) - `Total_duration_of_fixations.Disruptive_Person`,
    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations")), na.rm = TRUE) - `Number_of_fixations.Disruptive_Person`
  ) %>%
  ungroup() %>%
  summarise(
    Group = unique(Group),
    Average_duration_mtu = round(mean(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, na.rm = TRUE), 2),
    Number_fixation_mtu = sum(Total_fixations_excl_disruptive, na.rm = TRUE)
  ) %>%
  mutate(AOI = "MTU")

# Füge `Average_duration_mtu` und `Number_fixation_mtu` zur Langformat-Datenstruktur hinzu
df_aoi_avg_long <- bind_rows(df_aoi_avg_long, df_mtu_summary)

# Setze die AOIs in der gewünschten Reihenfolge, einschließlich "MTU"
df_aoi_avg_long <- df_aoi_avg_long %>%
  mutate(AOI = factor(AOI, levels = c(
    "MTU", "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
    "Board_Screen", "Material_Teacher", "Material_Students", 
    "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"
  ))) %>%
  arrange(AOI)

# Berechne deskriptive Statistiken, einschließlich "MTU"
aois_descriptives_durations <- df_aoi_avg_long %>%
  group_by(Group, AOI) %>%
  summarise(
    N = n(),
    M = round(mean(Average_duration, na.rm = TRUE), 2),
    SD = round(sd(Average_duration, na.rm = TRUE), 2),
    Min = round(min(Average_duration, na.rm = TRUE), 2),
    Max = round(max(Average_duration, na.rm = TRUE), 2)
  )

# Visualisierung: Boxplot der durchschnittlichen Fixationsdauer für alle AOIs
ggplot(df_aoi_avg_long, aes(x = AOI, y = Average_duration, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.15),
    size = 1.5,
    alpha = 0.7
  ) +
  scale_fill_brewer(palette = "RdBu") +
  labs(x = "AOI", y = "Average Duration of Fixations (ms)") +
  ggtitle("Average Duration of Fixations across all AOIs") +
  theme_minimal() +
  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))

# Ausgabe der deskriptiven Tabelle, einschließlich "MTU"
knitr::kable(aois_descriptives_durations,
             caption = "N, M, SD, min & max duration of fixations in milliseconds (across all AOIs)")

>>>>

### Check variables

@@

df_aoi_long <- df_aoi_filtered %>%
  rowwise() %>%
  mutate(
    across(starts_with("Number_of_fixations"), ~ .x / Duration_of_interval_min, .names = "fixation_per_min_{.col}")
  ) %>%
  ungroup() %>%
  pivot_longer(
    cols = starts_with("fixation_per_min_Number_of_fixations"),
    names_to = "AOI",
    values_to = "Fixations_per_minute"
  ) %>%
  mutate(AOI = str_remove(AOI, "fixation_per_min_Number_of_fixations.")) %>%
  mutate(AOI = factor(AOI, levels = c("Students", "Anna", "Bianca", "Carl(a)", "Disruptive_Person", 
                                      "Board_Screen", "Material_Teacher", "Material_Students", 
                                      "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"))) %>%
  arrange(AOI)

@@

knitr::kable(aois_descriptives_fixations,
             caption = "N, M, SD, min & max number of fixation per minute (across all AOIs)")

@@

# Filter and select necessary columns
df_aoi_filtered <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations")
  )

# Create a new AOI 'Students' by summing durations and counts for Anna, Bianca, and Carl(a)
df_aoi_filtered <- df_aoi_filtered %>%
  mutate(
    Total_duration_of_fixations.Students = 
      `Total_duration_of_fixations.Anna` +
      `Total_duration_of_fixations.Bianca` +
      `Total_duration_of_fixations.Carl(a)`,
    Number_of_fixations.Students = 
      `Number_of_fixations.Anna` +
      `Number_of_fixations.Bianca` +
      `Number_of_fixations.Carl(a)`,

    # Calculate Average Duration for all AOIs, excluding "Disruptive_Person"
    Total_duration_excl_disruptive = sum(c_across(starts_with("Total_duration_of_fixations"))[!names(c_across(starts_with("Total_duration_of_fixations"))) == "Total_duration_of_fixations.Disruptive_Person"], na.rm = TRUE),
    Total_fixations_excl_disruptive = sum(c_across(starts_with("Number_of_fixations"))[!names(c_across(starts_with("Number_of_fixations"))) == "Number_of_fixations.Disruptive_Person"], na.rm = TRUE),
    Average_duration_all = round(Total_duration_excl_disruptive / Total_fixations_excl_disruptive, digits = 2)  # Overall average duration
  )

# Calculate average fixation duration for each AOI individually, excluding disruptive person
df_aoi_avg_long <- df_aoi_filtered %>%
  pivot_longer(
    cols = starts_with("Total_duration_of_fixations") | starts_with("Number_of_fixations"),
    names_to = "Measure_AOI",
    values_to = "Values"
  ) %>%
  separate(Measure_AOI, into = c("Measure", "AOI"), sep = "\\.", extra = "merge") %>%
  pivot_wider(
    names_from = Measure,
    values_from = Values
  ) %>%
  filter(AOI != "Disruptive_Person") %>%
  mutate(
    Average_duration = round(Total_duration_of_fixations / Number_of_fixations, digits = 2)
  )

# Set the order of AOIs based on the specified sequence
df_aoi_avg_long <- df_aoi_avg_long %>%
  mutate(AOI = factor(AOI, levels = c(
    "Students", "Anna", "Bianca", "Carl(a)", "Disruptive_person", 
    "Board_Screen", "Material_Teacher", "Material_Students", 
    "Classroom_Others", "Nametag_Anna", "Nametag_Bianca", "Nametag_Carl(a)"
  ))) %>%
  arrange(AOI)

# Summarize descriptives for average duration of fixations
aois_descriptives_durations <- df_aoi_avg_long %>%
  group_by(Group, AOI) %>%
  summarise(
    N = n(),
    M = round(mean(Average_duration, na.rm = TRUE), 2),
    SD = round(sd(Average_duration, na.rm = TRUE), 2),
    Min = round(min(Average_duration, na.rm = TRUE), 2),
    Max = round(max(Average_duration, na.rm = TRUE), 2)
  )

knitr::kable(aois_descriptives_durations,
             caption = "N, M, SD, min & max duration of fixation per minute (across all AOIs)")

# Visualization: Boxplot for average duration of fixations across AOIs
ggplot(df_aoi_avg_long, aes(x = AOI, y = Average_duration, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(
    position = position_jitterdodge(jitter.width = 0.15),
    size = 1.5,
    alpha = 0.7
  ) +
  ylim(0, 1500) +
  scale_fill_brewer(palette = "RdBu") +
  labs(x = "AOI", y = "Average Duration of Fixations (ms)") +
  ggtitle("Average Duration of Fixations across all AOIs") +
  theme_minimal() +
  theme(legend.position = "top", axis.text.x = element_text(angle = 45, hjust = 1))
